The \kepler Smear Campaign I: An Asteroseismic Catalogue of Bright Red Giants

### 2018-09-12 paper/ms.tex
simon murphy section

Amongst our sample are pulsating stars of spectral type~B,~A, and~F, with their names, properties and variability class listed in Table~\ref{all_stars}.

Several stars have a more complex classification than can be adequately noted in Table~\ref{all_stars}: HD~189684 is listed as an ellipsoidal variable, but also shows evidence for $\gamma$\,Dor variability. HD~185397 and HD~186255 are listed as $\gamma$\,Dor/$\delta$\,Sct hybrids, but may in fact simply be $\delta$\,Sct variables with nonlinear combination frequencies, and a detailed frequency analysis will be required to distinguish between these possibilities. HD~184788 shows acombination of two rotational modulation signals with base frequencies: 0.0885 and~$0.1966 c/d$. HD~184875 is a $\gamma$\,Dor but also shows evidence for an unknown contaminant. V554~Lyr and V2079~Cyg are both known $\alpha^2$\,CVn variables, which are chemically peculiar stars with strong magnetic fields that show rotational modulation. V2079~Cyg also shows a weak $\delta$\,Sct signal. The detection of rotational modulation in the chemically-peculiar HD~175132 suggests its reclassification as an $\alpha^2$\,CVn variable.

>>>>

Our sample includes pulsating stars of spectral type~B,~A, and~F, with their names, properties and variability class listed in Table~\ref{all_stars}.

Among the hot-star sample are 5 $\delta$\,Sct stars, which show p-mode pulsation. These oscillation modes have particularly long lifetimes and stable frequencies, making them precise stellar clocks with periods of $\sim$2\,hr. These can be used to search for binarity and to obtain orbital parameters from photometry alone \citep{shibahashi&kurtz2012}. We used the phase-modulation method of \citet{murphyetal2014} to investigate whether any of these $\delta$\,Sct stars were binaries. Any phase modulation is converted into a light arrival-time delay, and if a star is a binary, the time delays of each mode should vary in unison. Nearly 350 PM binaries are known in the full \textit{Kepler} dataset \citep{murphyetal2018}.

In four of the five targets we found evidence for binarity, while in the fifth (HD\,185397) there was some time-delay variation but there was no agreement between different modes so it is not of binary origin. Of the others, HD\,175841 and HD\,177781 are likely very long-period binaries, with periods far exceeding the Kepler datasets of $\sim$1470\,d. HD\,181521 appears to be an eccentric binary with a period of at least 1000\,d, but there is only 1 maximum and 1 minimum in the time-delay curve (cf. \citep{murphy&shibahashi2015}), so a unique orbital solution was unobtainable. Finally, HD\,186255 is likely a binary with a period of $\sim$415\,d, but there is a slight aperiodicity in the time delays, likely caused by beating between pulsation modes that are not well-separated in the frequency. That, coupled with the fact that this star is on the failed Module 3 and is therefore missing data every 4th quarter (i.e. $\sim$93 of every 372.5\,d), makes the binary classification uncertain. If indeed this is a 415-d binary, the time delays are consistent with a companion of minimum mass $\sim$0.45\,M$_{\odot}$ in an orbit of moderate eccentricity ($\sim$0.15).

Several stars have a more complex classification than can be adequately noted in Table~\ref{all_stars}: HD~189684 is listed as an ellipsoidal variable, but also shows evidence for $\gamma$\,Dor variability. HD~185397 and HD~186255 are listed as $\gamma$\,Dor/$\delta$\,Sct hybrids, but may in fact simply be $\delta$\,Sct variables with nonlinear combination frequencies, and a detailed frequency analysis will be required to distinguish between these possibilities. HD~184788 shows a combination of two rotational modulation signals with base frequencies: 0.0885 and~$0.1966 c/d$. HD~184875 is a $\gamma$\,Dor but also shows evidence for an unknown contaminant. V554~Lyr and V2079~Cyg are both known $\alpha^2$\,CVn variables, which are chemically peculiar stars with strong magnetic fields that show rotational modulation. V2079~Cyg also shows a weak $\delta$\,Sct signal. The detection of rotational modulation in the chemically-peculiar HD~175132 suggests its reclassification as an $\alpha^2$\,CVn variable.
